Report on the Second Workshop on Sustainable Software for Science: Practice and Experiences (WSSSPE2)

### 2015-04-03 WSSSPE2_report/WSSSPE2_review.tex
Appendix A: Add a TODO.
Section 4: Add a note from discussion with Dan.

\begin{comment}  
gvwilson@software-carpentry.org, Colin Venters <C.Venters@hud.ac.uk>,
j.spencer@imperial.ac.uk, erinrobinson@esipfed.org, marpierc@iu.edu,
jwpeterson@gmail.com, abani@buffalo.edu, clenhardt@renci.org, dsk@uchicago.edu,
Samin.Ishtiaq@microsoft.com, james@howison.name, s.a.harris@leeds.ac.uk,
marcus.hanwell@kitware.com, thabermann@hdfgroup.org, rdowns@ciesin.columbia.edu,
cboettig@gmail.com, jakob.blomer@cern.ch, editor@ascl.net 
\end{comment}

@@

>>>>

\note{
Lighting talks, breakout groups, working groups are all different. Lightning
talks were new in WSSSPE2. They were offered to all paper contributors, and some
other attendees, those who got travel awards. Breakout groups in WSSSPE1 were
just discussions about topics; in WSSSPE2, the breakout groups were supposed to
come up with plans for actions in specific areas. The idea of working groups is
that they will come out of breakout groups as a way for the groups to actually
do the actions over time, not at the workshops.
}

\begin{comment}  
Email addresses of speakers:
gvwilson@software-carpentry.org, Colin Venters <C.Venters@hud.ac.uk>,
j.spencer@imperial.ac.uk, erinrobinson@esipfed.org, marpierc@iu.edu,
jwpeterson@gmail.com, abani@buffalo.edu, clenhardt@renci.org, dsk@uchicago.edu,
Samin.Ishtiaq@microsoft.com, james@howison.name, s.a.harris@leeds.ac.uk,
marcus.hanwell@kitware.com, thabermann@hdfgroup.org, rdowns@ciesin.columbia.edu,
cboettig@gmail.com, jakob.blomer@cern.ch, editor@ascl.net 
\end{comment}

@@

\choinote{Add missing speaker names}
